\documentclass[margin, line, 11pt]{res} 
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{stack}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{bold-extra}
\usepackage{lmodern}
\usepackage[super]{nth}

\hypersetup{colorlinks=true, urlcolor=blue}
\newsectionwidth{1.0in}
\renewcommand{\labelitemi}{\textendash}

\begin{document}

\noindent\hspace{-1.0in}{\LARGE\bf Aurora Siegel}
\hfill \href{mailto:aurora.fay92@gmail.com}{aurora.fay92@gmail.com}
$\cdot$ 770-617-9786
$\cdot$ \href{http://aurorasiegel.com}{aurorasiegel.com}

\begin{resume}

\section{SUMMARY}

A driven and creative problem solver looking for an opportunity in data analysis, especially where I can apply my UX research, programming, and statistical skills. 

\section{EDUCATION}

{\bf Queens College} $\cdot$ {\it M.A. Data Analytics and Applied Social Research} \hfill \texttt{June 2018}
\\{\it  Major GPA}: 3.72
\\{\it Graduate Thesis}: Utilizing Feelings Towards Groups for Improved Voter Prediction
\\{\it Coursework}: Computational Social Science, Advanced Analytics, Data Structures, Discrete 
Mathematics, Object Oriented Programming in Java \& C++.

{\bf Georgia State University} $\cdot$ {\it B.A. Women's, Gender, and Sexuality Studies} \hfill \texttt{May 2014}

{\bf YCombinator} $\cdot$ {\it Startup School working on \href{http://silverfoxens.com}{SilverFoxens.com}}\hfill \texttt{Aug 2018 $\rightarrow$ Dec 2018}
\begin{itemize}
  \item Personally surveyed interested individuals, online and offline, about their companionship needs and online dating usage.
  \item Developed a website, database, user recommendation system together, and various usability and safety features with a software engineer.
\end{itemize}
{\bf Udacity} $\cdot$ {\it \href{https://confirm.udacity.com/VUHFGNF6}{Front-End Web Developer Nanodegree}} \hfill \texttt{Apr 2019}
\\ {\bf Udacity} $\cdot$ {\it Data Analyst Nanodegree} \hfill \texttt{Dec 2018 $\rightarrow$  Present}

\section{SKILLS}

\begin{description}
\item[Programming:] Python, R, SQL, Javascript, HTML, CSS, \LaTeX
\item[Tools:] Git, Linux, AWS, DigitalOcean, Google Analytics, Excel, SSH
\item[Analysis:] Cross-Tabulation, Logistic Regression, ANOVA, t-Test, Text Analysis, LDA
\end{description}

\section{EXPERIENCE}

{\bf QuinStreet}\vspace{0.04in}
\\ {\it Vertical Marketing Analyst} $\cdot$ San Francisco, CA \hfill\texttt{Feb 2019 $\to$ Present}\vspace{0.04in}
\begin{itemize}
\item Onboard clients, measure and track advertising metrics.
\end{itemize}

{\bf Queens College}\vspace{0.04in}
\\ {\it Graduate Research Assistant} $\cdot$ New York City, NY \hfill\texttt{August 2016 $\to$ June 2018}\vspace{0.04in}
\begin{itemize}
\item Methodically cleaned an academic paper dataset and categorized research papers. Investigated the signal between gender and writing style using various text analysis methods. 
\item As part of research thesis I uncovered strong signals between questions about voter feelings towards current events and their voting behavior. Developed approaches that could potentially lead to better election prediction than asking voters directly who they will vote for, particularly in controversial elections.
\end{itemize}

{\bf Aids Center of Queens County}\vspace{0.04in}
\\ {\it Administrative Assistant} $\cdot$ New York City, NY \hfill\texttt{October 2014 $\to$ December 2016}\vspace{0.04in}
\begin{itemize}
\item Worked with the Finance \& Legal departments on various duties.
\item Took ownership over the audit preparation process. Reduced client follow-up interviews by 20\% by revamping client forms that sped up data input.
\end{itemize}

\end{resume}

\hfill{Last updated January 2019}

\end{document}
